%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{setspace}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{lastpage}
\usepackage{geometry}
\usepackage{fancyref}
\usepackage{nameref}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\makeatletter
\let\orgdescriptionlabel\descriptionlabel
\renewcommand*{\descriptionlabel}[1]{%
  \let\orglabel\label
  \let\label\@gobble
  \phantomsection
  \edef\@currentlabel{#1}%
  \let\label\orglabel
  \orgdescriptionlabel{#1}%
}
\makeatother

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\geometry{letterpaper,left=1cm,right=1cm,top=1cm, bottom=1cm}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small{#2} \\
      \textit{\small#3} & {\small #4}
    \end{tabular*}
    \vspace{-2pt}
}
\newcommand{\projtitle}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{- }\textit{#1} & {\small #2} \\
    \end{tabular*}
    \vspace{-5pt}
}
\newcommand{\projcontent}[1]{\vspace{-1pt}\textbf{- }{\small #1}\vspace{-3pt}}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{enumerate}[label=\arabic*., leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{enumerate}\vspace{-2pt}}
\newcommand{\resumeItemListStart}{\vspace{-2pt}\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\justifying
%----------HEADING-----------------
\begin{center}
  \textbf{\Large Yun Chen} \\
  \vspace{2pt}
  \small
  \faMapMarker*~San Diego, CA \ \ $|$ \ \
  \faEnvelope~\href{mailto:yunchen@qti.qualcomm.com}{yunchen@qti.qualcomm.com} \ \ $|$ \ \
  \faGlobe~\url{yunchen011.github.io} \ \ $|$ \ \
  \faLinkedin~\url{linkedin.com/in/yun-chen-site}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
\resumeItemListStart
\resumeSubheading
      {University of California San Diego (UCSD)}{San Diego, CA}
      {Ph.D., Electrical and Computer Engineering (Degree Conferred)}{Apr. 2024 - Apr. 2025}
\resumeSubheading
      {North Carolina State University (NCSU)}{Raleigh, NC}
      {Ph.D. Program, Electrical and Computer Engineering (GPA: 4.0/4.0) -- transferred to UCSD}{Jan. 2021 - Mar. 2024}
\resumeSubheading
      {The University of Texas at Austin (UT Austin)}{Austin, TX}
      {M.S., Electrical and Computer Engineering (GPA: 3.95/4.0)}{Aug. 2018 - Dec. 2020}
\resumeSubheading
      {Southeast University}{Nanjing, China}
      {Bachelor of Engineering in Information Engineering (GPA: 89.13/100)}{Aug. 2013 - Jun. 2017}
\resumeItemListEnd


%-----------EXPERIENCE-----------------
\section{Research and Industry Experience}

\vspace{2pt}\noindent\textbf{\textit{Industry Experience}}
    \resumeItemListStart

\resumeSubheading{Senior Engineer}{Apr. 2025 - Present}
     {Qualcomm Technologies, Inc.}{}
     \resumeItemListStart
       \resumeSubItem{}{Full-time engineering role, building on Ph.D. research and prior Qualcomm internships}
     \resumeItemListEnd

\resumeSubheading{Engineering Intern}{Summers 2021, 2022 \& 2023}
     {Qualcomm Technologies, Inc.}{}
     \resumeItemListStart
       % ML-based detection and localization for indoor device-free RF sensing
       \resumeSubItem{}{ML-based detection and localization for indoor device-free RF sensing -- Dr. Marwen Zorgui, Dr. Arumugam Kannan (2023)}
       % Precise indoor positioning using semi-supervised learning
       \resumeSubItem{}{Precise indoor positioning using semi-supervised learning -- Dr. Srinivas Yerramalli (2022)}
       % ML assisted coordinated multi-point transmission for ultra-reliable services
       \resumeSubItem{}{ML-assisted coordinated multi-point transmission for ultra-reliable services -- Dr. Taesang Yoo (2021)}
     \resumeItemListEnd

\resumeSubheading{Research Intern}{Summers 2019 \& 2020}
     {Ericsson Inc. -- Prof. Ali Khayrallah}{}
     \resumeItemListStart
       % Optimizations for A2G network deployments for high user throughput
       \resumeSubItem{}{Deep learning-based 5G air-to-ground network design and optimization [\ref{pub:S1}][\ref{pub:C1b}] (2020)}
       % Handover management for UAVs using Q-learning and deep Q-network
       \resumeSubItem{}{Reinforcement-learning-based drone mobility and handover management [\ref{pub:C1a}][\ref{pub:C0a}] (2019)}
     \resumeItemListEnd

    \resumeItemListEnd

\vspace{4pt}\noindent\textbf{\textit{Academic Research}}
    \resumeItemListStart

\resumeSubheading{Graduate Researcher}{Sep. 2019 - Mar. 2025}
     {WiSeCom Lab / UT Austin, NC State University, UC San Diego -- Prof. Nuria Gonz\'{a}lez Prelcic}{}
     \resumeItemListStart
       \resumeSubItem{}{Hybrid model/data-driven mmWave localization, channel estimation, and user tracking for ISAC systems}
       \resumeSubItem{}{Attention-network-based vehicle position and channel tracking at mmWave [\ref{pub:J3}][\ref{pub:J2}][\ref{pub:C4}]}
       \resumeSubItem{}{Collaborative V2V sidelink localization for orientation estimation and position tracking [\ref{pub:C7}]}
       \resumeSubItem{}{Low-complexity mmWave channel estimation via ESPRIT-D [\ref{pub:C5}]}
       \resumeSubItem{}{Radar-to-communication channel mapping for mmWave link configuration [\ref{pub:B1}][\ref{pub:J1}][\ref{pub:C2}]}
       \resumeSubItem{}{UAV navigation using a monocular camera and deep reinforcement learning [\ref{pub:C0b}]}
     \resumeItemListEnd

\resumeSubheading{Undergraduate Research Assistant}{Jan. 2017 - Jun. 2017}
     {Southeast University -- Prof. Luxi Yang, Prof. Chunguo Li}{}
     \resumeItemListStart
       % Trajectory optimizations for bicycle travelers using Q-learning
       \resumeSubItem{}{Trajectory optimization for bicycle trip planning using reinforcement learning [\ref{pub:Ce}]}
       % Cloud cache management using transfer learning
       \resumeSubItem{}{Proactive caching in wireless networks using transfer learning [\ref{pub:Cf}]}
       % Mobile edge computing resource allocation using an Echo State Network
       \resumeSubItem{}{Mobile edge computing resource allocation using an Echo State Network}
     \resumeItemListEnd

    \resumeItemListEnd

\section{Patents}
\resumeItemListStart
  \resumeSubItem{}{X. Lin, \textbf{Y. Chen}, M. Mozaffari, T. Khan, ``Efficient 3D Mobility Support Using Reinforcement Learning''. US20240056933A1. Feb.
2024}\label{pat:P1}
  \resumeSubItem{}{M. Mozaffari, X. Lin,  T. Khan, M. Afshang, \textbf{Y. Chen}, ``Network Design and Optimization Using Deep Learning''. US20230388196A1. Nov. 2023}\label{pat:P2}
\resumeItemListEnd

\section{Publications}
  \resumeSubHeadingListStart

  \resumeSubItem{}{\textbf{Y. Chen}, ``Hybrid Model/Data-Driven Solutions in ISAC: Improving Link Establishment, Channel Estimation, and User Localization in mmWave Vehicular Networks", Ph.D. Dissertation, University of California San Diego, Advisor: Prof. Nuria Gonz\'{a}lez-Prelcic, 2026, pending release.}\label{pub:D1}

  \resumeSubItem{}{\textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, T. Shimizu, C. Mahabal, ``A Hybrid Model/Data-Driven Solution to Channel, Position, and Orientation Tracking in mmWave Vehicular Systems", \emph{IEEE Journal on Selected Areas in Communications}, vol. 44, pp. 927--941, 2026.}\label{pub:J3}

  \resumeSubItem{}{S. Javid, \textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, ``Learning-Based Cross-Frequency Channel Prediction in the Upper Mid-band", in \emph{IEEE Global Communications Conference (GLOBECOM 2025)}, pp. 6394--6399, Dec. 2025.}\label{pub:C8}

  \resumeSubItem{}{\textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, T. Shimizu, C. Mahabal, ``Collaborative Position and Orientation Tracking in mmWave Vehicular Systems Exploiting V2I and V2V Links", in \emph{2024 58th Asilomar Conference on Signals, Systems, and Computers}, pp. 407--412, Oct. 2024.}\label{pub:C7}

  \resumeSubItem{}{B. Kumar, \textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, T. Shimizu, A. Ganlath, ``DeepSatLoc: A Multimodal Fusion Strategy for Enhanced Localization in Urban Canyons Exploiting GPS and LEO Satellite Communication Signals", in \emph{2024 58th Asilomar Conference on Signals, Systems, and Computers}, pp. 842--849, Oct. 2024.}\label{pub:C6}

  \resumeSubItem{}{\textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, T. Shimizu, H. Lu, C. Mahabal, ``Beamspace ESPRIT-D for Joint 3D Angle and Delay Estimation for Joint Localization and Communication at MmWave", in \emph{IEEE International Conference on Communications (ICC 2024)}, pp. 1915--1920, Jun. 2024.}\label{pub:C5}

  \resumeSubItem{}{\textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, T. Shimizu, H. Lu, ``Learning to Localize with Attention: from sparse mmWave channel estimates from a single BS to high accuracy 3D location", \emph{arXiv:2307.00167}, Jun. 2023, revised Mar. 2025.}\label{pub:J2}

  \resumeSubItem{}{\textbf{[Best Student Paper]} \textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, T. Shimizu, H. Lu, C. Mahabal, ``Sparse Recovery with Attention: A Hybrid Data/Model Driven Solution for High Accuracy Position and Channel Tracking at mmWave", in \emph{2023 IEEE 24th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC)}, pp. 491--495, Sep. 2023.}\label{pub:C4}

  \resumeSubItem{}{N. Gonz\'{a}lez-Prelcic, A. Ali, \textbf{Y. Chen}, ``Radar-Aided Millimeter Wave Communication", in \emph{Signal Processing for Joint Radar Communications}, Wiley-IEEE Press, pp. 155--177, Mar. 2024.}\label{pub:B1}

  \resumeSubItem{}{A. Graff, \textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, T. Shimizu, ``Deep Learning-Based Link Configuration for Radar-Aided Multiuser mmWave Vehicle-to-Infrastructure Communication", \emph{IEEE Transactions on Vehicular Technology}, vol. 72, no. 6, pp. 7454--7468, Jun. 2023.}\label{pub:J1}

  \resumeSubItem{}{\textbf{Y. Chen}, J. Palacios, N. Gonz\'{a}lez-Prelcic, T. Shimizu, H. Lu, ``Joint Initial Access and Localization in Millimeter Wave Vehicular Networks: a Hybrid Model/Data Driven Approach", in \emph{2022 IEEE 12th Sensor Array and Multichannel Signal Processing Workshop (SAM)}, pp. 355--359, Jun. 2022.}\label{pub:C3}

  \resumeSubItem{}{G. Geraci, A. Garcia-Rodriguez, M. Azari, A. Lozano, M. Mezzavilla, S. Chatzinotas, \textbf{Y. Chen}, S. Rangan, M. Renzo, ``What Will the Future of UAV Cellular Communications Be? A Flight From 5G to 6G", \emph{IEEE Communications Surveys \& Tutorials}, vol. 24, no. 3, pp. 1304--1335, 2022.}\label{pub:S1}

  \resumeSubItem{}{\textbf{Y. Chen}, A. Graff, N. Gonz\'{a}lez-Prelcic, T. Shimizu, ``Radar Aided mmWave Vehicle-to-Infrastructure Link Configuration Using Deep Learning", in \emph{2021 IEEE Global Communications Conference (GLOBECOM)}, pp. 1--6, Dec. 2021.}\label{pub:C2}

  \resumeSubItem{}{\textbf{Y. Chen}, X. Lin, T. Khan, M. Afshang, M. Mozaffari, ``5G Air-to-Ground Network Design and Optimization: A Deep Learning Approach", in \emph{2021 IEEE 93rd Vehicular Technology Conference (VTC2021-Spring)}, pp. 1--6, Apr. 2021.}\label{pub:C1b}

  \resumeSubItem{}{\textbf{Y. Chen}, X. Lin, T. Khan, M. Mozaffari, ``A Deep Learning Approach to Efficient Drone Mobility Support", in \emph{Proceedings of the 2nd ACM MobiCom Workshop on Drone Assisted Wireless Communications for 5G and Beyond}, pp. 67--72, Sep. 2020.}\label{pub:C1a}

  \resumeSubItem{}{\textbf{Y. Chen}, N. Gonz\'{a}lez-Prelcic, R. W. Heath, ``Collision-Free UAV Navigation with a Monocular Camera Using Deep Reinforcement Learning", in \emph{2020 IEEE 30th International Workshop on Machine Learning for Signal Processing (MLSP)}, pp. 1--6, Sep. 2020.}\label{pub:C0b}

  \resumeSubItem{}{\textbf{[Best Paper]} \textbf{Y. Chen}, X. Lin, T. Khan, M. Mozaffari, ``Efficient Drone Mobility Support Using Reinforcement Learning'', in \emph{2020 IEEE Wireless Communications and Networking Conference (WCNC)}, pp. 1--6, May 2020.}\label{pub:C0a}

  \resumeSubItem{}{\textbf{Y. Chen}, W. Yan, C. Li, Y. Huang, and L. Yang, ``Personalized Optimal Bicycle Trip Planning Based on Q-learning Algorithm'', in \emph{2018 IEEE Wireless Communications and Networking Conference (WCNC)}, pp. 1--6, Apr. 2018.}\label{pub:Ce}

  \resumeSubItem{}{Y. Wang, \textbf{Y. Chen}, H. Dai, Y. Huang, and L. Yang, ``A Learning-Based Approach for Proactive Caching in Wireless Communication Networks'', in \emph{2017 9th International Conference on Wireless Communications and Signal Processing (WCSP)}, pp. 1--6, Oct. 2017.}\label{pub:Cf}

\resumeSubHeadingListEnd


\section{Teaching Experience}
  \resumeItemListStart
    \resumeSubheading
      {Teaching Assistant}{Winter 2025}
      {Circuits and Systems, UC San Diego - Prof. Robert Heath}{}
    \resumeSubheading
      {Teaching Assistant}{Spring 2019}
      {Probability and Random Process, UT Austin - Prof. Pedro Santacruz}{}
  \resumeItemListEnd

%---------Honors & Awards------------
\section{Honors and Awards}

\resumeItemListStart
\resumeSubItem{}{Best Student Paper Award in \textit{IEEE SPAWC 2023}
\hfill
Sep. 2023
}
\resumeSubItem{}{Summer Graduate Fellowship of the College of Engineering at NCSU
\hfill
May 2022
}

\resumeSubItem{}{\href{https://wcnc2020.ieee-wcnc.org/program/ieee-wcnc-2020-best-paper-selection}{Best Paper Award} in \textit{IEEE WCNC 2020} (Top 4 out of 400 accepted papers)
\hfill
May 2020
}
\resumeSubItem{}{Excellent Graduation Project at SEU (Top 10 out of 260 projects)
\hfill
Jun. 2017
}
 \resumeSubItem{}
 {Honorable Mention in the Mathematical Contest in Modeling (MCM)
      \hfill
      Apr. 2016
}
 \resumeSubItem{}{Leike Scholarship at SEU (Top 5\% out of 1600 students)
\hfill
Jun. 2015
}
 \resumeSubItem{}{$2^{nd}$ Prize out of 1,000 students in Provincial Advanced Mathematics Competition
\hfill
Jun. 2014
}

\resumeItemListEnd

%--------PROGRAMMING SKILLS------------
\section{Professional Skills}
\resumeItemListStart
\resumeSubItem{}
{\textbf{Skills}:}

\projcontent{Programming languages: Python, Matlab, C++, HTML}

\projcontent{Platforms: PyTorch, Tensorflow}

\projcontent{Simulation tools: Wireless Insite, Robot Operating System (ROS)}

\resumeSubItem{}
      {\textbf{Language}{: English (fluent), Mandarin (native)}}

  \resumeItemListEnd


%-------------------------------------------
\end{document}
